Acceleration of Global Search by Implementing Dual Estimates for Lipschitz Constant\thanks{This research was supported by the Russian Science Foundation, project No.\,16-11-10150.}

### 2019-09-12 2019/NUMTA_Barkalov/LNCS/numta19.tex
Reliabiliry

\item
For each interval $(x_{i-1}, x_i), \; 1\leq i \leq k,$  calculate the value 
$R(i)$ called the \textit{characteristic} of the interval
\begin{equation}\label{R}
R(i)=\Delta_i+\frac{(z_i-z_{i-1})^2}{r^2\mu^2\Delta_i}-2\frac{z_i+z_{i-1}-2z^*}{r\mu},
\end{equation}
where 
\begin{equation}\label{z}
z^*= \min_{0\leq i\leq k}z_i
\end{equation} 
and the real number $r>1$ is 
the input parameter of the algorithm.
\item 
Select the interval $(x_{t-1},x_t)$ corresponding to the maximum characteristic
\begin{equation}\label{MaxR}
R(t)= \max_{1 \leq i \leq k}R(i).
\end{equation}
\item
Carry out the next trial at the point $x^{k+1}\in(x_{t-1},x_t)$ calculated using
the following formula
\begin{equation}\label{xk1}
x^{k+1} = \frac{x_t+x_{t-1}}{2} - \mathrm{sign}(z_t-z_{t-1})\frac{1}{2r}
\left[\frac{\left|z_t-z_{t-1}\right|}{\mu}\right]^N.
\end{equation}
\end{enumerate}

@@

An approach, in which two estimates of the Lipschitz constant %, one of which is essentially greater than another, 
are used in the rules of the algorithm, seems quite promising. 
This approach implies the use in the algorithm of two parameters $r_{glob}$ and $r_{loc}$, where $r_{glob} > r_{loc}>1$.

>>>>

\item
For each interval $(x_{i-1}, x_i), \; 1\leq i \leq k,$  calculate the value 
$R(i)$ called the \textit{characteristic} of the interval
\begin{equation}\label{R}
R(i)=\Delta_i+\frac{(z_i-z_{i-1})^2}{r^2\mu^2\Delta_i}-2\frac{z_i+z_{i-1}-2z^*}{r\mu},
\end{equation}
where 
\begin{equation}\label{z}
z^*= \min_{0\leq i\leq k}z_i
\end{equation} 
and the real number $r>1$ is a reliability parameter of the algorithm.
\item 
Select the interval $(x_{t-1},x_t)$ corresponding to the maximum characteristic
\begin{equation}\label{MaxR}
R(t)= \max_{1 \leq i \leq k}R(i).
\end{equation}
\item
Carry out the next trial at the point $x^{k+1}\in(x_{t-1},x_t)$ calculated using
the following formula
\begin{equation}\label{xk1}
x^{k+1} = \frac{x_t+x_{t-1}}{2} - \mathrm{sign}(z_t-z_{t-1})\frac{1}{2r}
\left[\frac{\left|z_t-z_{t-1}\right|}{\mu}\right]^N.
\end{equation}
\end{enumerate}

@@

An approach, in which two estimates of the Lipschitz constant are used in the rules of the algorithm, seems quite promising. 
This approach implies the use in the algorithm of two parameters $r_{glob}$ and $r_{loc}$, where $r_{glob} > r_{loc}>1$.
